---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

## Tracking My Daily Short Video Watching Habits

This dynamic report summarises data collected from my observational logging of daily short video watching sessions.

This report analyses how many videos were watched, how sessions were rated, what type of content was mostly watched, and what time of day the viewing happened.

```{r}
library(tidyverse)

logged_data <- read_csv(
  "https://docs.google.com/spreadsheets/d/e/2PACX-1vTZDCEDFuSOD-daLJTgA9o8ndZBu0fLPIPHLAqLcbNZrXhuOH3vQh9mMpdoRhoXVc1n0cTF4RfT9lRm/pub?output=csv",
  show_col_types = FALSE
)

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    num_videos = `How many videos did you watch in this session?`,
    content_type = `What type of content did you mostly watch?`,
    time_of_day = `What time of day was this?`,
    platform = `Which platform did you use?`,
    rating = `How would you rate this session?`
  )
```

### Dynamic summary comments

```{r}
total_sessions <- nrow(latest_data)
avg_videos <- mean(latest_data$num_videos)
avg_rating <- mean(latest_data$rating)
max_videos <- max(latest_data$num_videos)
```

The dataset currently contains `r total_sessions` observations.

On average, I watched `r round(avg_videos, 2)` videos per session.

The average session rating was `r round(avg_rating, 2)` out of 5.

The highest number of videos watched in one session was `r max_videos`.

### Bar chart: content type

```{r}
ggplot(latest_data, aes(x = content_type)) +
  geom_bar() +
  labs(
    title = "Types of Content Mostly Watched",
    x = "Content type",
    y = "Count"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Bar chart: time of day

```{r}
ggplot(latest_data, aes(x = time_of_day)) +
  geom_bar() +
  labs(
    title = "Time of Day of Video Watching Sessions",
    x = "Time of day",
    y = "Count"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```